---
title: "Data Import"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

This document will show how to import data. 

## Import the FAS Litters CVS 

(janitor: replace spaces with underscores, changed to lowercase (comm shift I for r chunk))

(instead of using whole library, just used clean name function from janitor package/library)
```{r}
litters_df = read_csv("data/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df)
```

### Look at the dataset 
(tail, but last 10 entries)
```{r}
litters_df

head(litters_df)
tail(litters_df, 10)
```

```{r eval = FALSE}
view(litters_df)
```


# Learning Assessment Sept 17
## Import the FAS pups 

Use relative paths.
```{r}
pups_df = read_csv("data/FAS_pups.csv")

pups_df = janitor::clean_names(pups_df)

pups_df
```

Use absolute path.
```{r, eval = FALSE}
pups_df = read_csv("/Users/shehzrin/Desktop/DataScience2024/data_wrangling_i/data/FAS_pups.csv")
```




## Look at read_csv options 

col_names and skipping rows

```{r}
litters_df = 
  read_csv(
    file = "data/FAS_litters.csv",
    col_names = FALSE,
    skip = 1
  )
```


What about missing data.
```{r}
litters_df =
  read_csv(
    file = "data/FAS_litters.csv",
    na = c("NA","",".")
  )
```

litters_df = janitor::clean_names(litters_df)

pull(litters_df, gd0_weight)

What if we code 'group' as a factor variable?
```{r}
litters_df = 
  read_csv(
    file = "data/FAS_litters.csv",
    na = c("NA","","."),
    col_types = cols(
      Group = col_factor()
    )
  )
```

import pups; missing values; column parsing

